### 2024-01-17 ms.qmd
Updates

### Subjects

@@

### Husbandry

@@

### CORT and Temperature manipulation
To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@FigMethods A). We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle. CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data). Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching. The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

### Learning

@@

### Statistical analyses
We performed the analyses with species (_L. delicata_ or _L. guichenoti_) and task ('Associative' or 'Reversal') separately. We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well. As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (**REF brm package**) in Quartos (**REF QUARTOS**). Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e. whether the individual chose correct (1) or not (0) was used as the response variable, employing a Bernoulli probability distribution (link=‘logit’). The fixed effects of the model included a triple interaction between: trial ('Associative trial' or 'Reversal trial') as a numeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors. For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial within each level of lizard identity. For all models we 
We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned. More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparissons between 'Treatments' (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

### Results
```{r, cleaning}
#| label: cleaning
source(here("R", "1_data_process.R"))
# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
```

@@

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
### Group = red
drr_CORTCold <- deli_rev_red$b_trial_reversal
drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
### Group = blue
drb_CORTCold <- deli_rev_blue$b_trial_reversal
drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
## 2) L. guichenoti
### Group = red
grr_CORTCold <- guich_rev_red$b_trial_reversal
grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
### Group = blue
grb_CORTCold <- guich_rev_blue$b_trial_reversal
grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
```
```{r, InterceptsRev}
```

@@

#| tbl-cap: "\beta estimates of Associative learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the /beta estimates obtain from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean /beta estimates is equal to zero. In bold those values that are significant (p-value <0.05)"

@@

asso_interval_975 <- format_dec(sapply(estimates_asso, function (x) quantile(x,0.975)), 3)

@@

rev_interval_975 <- format_dec(sapply(estimates_rev, function (x) quantile(x,0.975)), 3)

@@

@Tabledata summarizes the estimates of learning slopes for all the treatments in each model (see Statistical analyses). On average, we found that learning slopes were lower when the 'Blue' feeders were correct compared to those assigned to the group 'Red'  for _L. delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot))`), but not for _L. guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`). However, because we suspect there may be a bias towards 'Blue' in the initial choice (see Supplementary Material and Figs. @Figdeli, @Figguich), we only used those individuals assigned to 'Red' to compare performance in the associative learning task. In this regard, we did not find any significant differences between treatments for _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figduich).
When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`). We also did not find any significant differences when we compared the estimated slopes between species for the associative task (only individuals from 'Red' group: _L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).

## References

## Suplementary Material

### Colour preference in the Associative task
To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution. We get this intercepts for each species, group and treatment, and we estimated the probability of choosing right using the formula:

@@

  probright_drCORTCold = probright_drCORTCold,
  probright_drControlCold = probright_drControlCold,
  probright_drCORTHot = probright_drCORTHot,
  probright_drControlHot = probright_drControlHot,
  probright_dbCORTCold = probright_dbCORTCold,
  probright_dbControlCold = probright_dbControlCold,
  probright_dbCORTHot = probright_dbCORTHot,
  probright_dbControlHot = probright_dbControlHot,
  probright_grCORTCold = probright_grCORTCold,
  probright_grControlCold = probright_grControlCold,
  probright_grCORTHot = probright_grCORTHot,
  probright_grControlHot = probright_grControlHot,
  probright_gbCORTCold = probright_gbCORTCold,
  probright_gbControlCold = probright_gbControlCold,
  probright_gbCORTHot = probright_gbCORTHot,
  probright_gbControlHot = probright_gbControlHot
) %>% #This way we get a df with 16 variables
  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
  gather(key = "column", value = "value", .) %>% #To transpose the df

@@

                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%

@@

  pivot_wider(names_from = Group, values_from = c(value, column)) %>% #To split the df in Red and Blue

@@

# Then we build a df with the statistical comparison between probabilities (Blue minus Red) for each treatment and species and p-values for each comparison
comp_prob <- data.frame(
  (probright_dbCORTCold - probright_drCORTCold),
  (probright_dbControlCold - probright_drControlCold),
  (probright_dbCORTHot - probright_drCORTHot),
  (probright_dbControlHot - probright_drControlHot),
  (probright_gbCORTCold - probright_grCORTCold),
  (probright_gbControlCold - probright_grControlCold),
  (probright_gbCORTHot - probright_grCORTHot),
  (probright_gbControlHot - probright_grControlHot)
) %>% 
  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
  gather(key = "column", value = "value", .) %>% #To transpose the df
                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
  rename("[Blue - Red]" = "value") %>%
  pmcmc(probright_dbCORTCold - probright_drCORTCold),
  pmcmc(probright_dbControlCold - probright_drControlCold),
  pmcmc(probright_dbCORTHot - probright_drCORTHot),
  pmcmc(probright_dbControlHot - probright_drControlHot),
  pmcmc(probright_gbCORTCold - probright_grCORTCold),
  pmcmc(probright_gbControlCold - probright_grControlCold),
  pmcmc(probright_gbCORTHot - probright_grCORTHot),
  pmcmc(probright_gbControlHot - probright_grControlHot)
) %>% 
  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
  gather(key = "column", value = "value", .) %>% #To transpose the df
                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
  rename("p-value" = "value") %>%
#Create the final database and the table
table_df <- merge(prob_df, comp_prob, by = c("Specie", "Treatment")) %>%
  merge(comp_pval, by = c("Specie", "Treatment")) %>%
  select(Specie, Treatment, value_Blue, value_Red, X.Blue...Red., p.value) %>%
table_df <- table_df %>%

@@

  bold(~ `p.value` < 0.05, ~ `p.value` + X.Blue...Red.) %>%

@@

  set_header_labels(value_Blue = "Blue",
                    value_Red = "Red",
                    p.value = "p-value",
                    X.Blue...Red. = "[Blue - Red]") %>%
  colformat_num(columns = c("Blue", "Red", "[Blue-Red]", "p-value"), digits = 3) %>% # To set the number of decimals

@@

>>>>

#### Subjects

@@

#### Husbandry

@@

#### CORT and Temperature manipulation
To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@FigMethods A). We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle. CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data). Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching. The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

#### Learning

@@

#### Statistical analyses
We performed the analyses with species (_L. delicata_ or _L. guichenoti_) and task ('Associative' or 'Reversal') separately. We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well. As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (**REF brm package**) in Quartos (**REF QUARTOS**). Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e. whether the individual chose correct (1) or not (0) was used as the response variable, employing a Bernoulli probability distribution (link=‘logit’). The fixed effects of the model included a triple interaction between: trial ('Associative trial' or 'Reversal trial') as a numeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors. For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial within each level of lizard identity. For all models we 
We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned. More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparissons between 'Treatments' (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

## Results
```{r, cleaning}
#| label: cleaning
source(here("R", "1_data_process.R"))
# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
```

@@

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
### Group = red
drr_CORTCold <- deli_rev_red$b_trial_reversal
drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
### Group = blue
drb_CORTCold <- deli_rev_blue$b_trial_reversal
drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
## 2) L. guichenoti
### Group = red
grr_CORTCold <- guich_rev_red$b_trial_reversal
grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
### Group = blue
grb_CORTCold <- guich_rev_blue$b_trial_reversal
grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
```

@@

#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"

@@

asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)

@@

rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)

@@

@Tabledata summarizes the estimates of learning slopes for all the treatments in each model (see Statistical analyses). On average, we found that learning slopes were lower when the 'Blue' feeders were correct compared to those assigned to the group 'Red'  for _L. delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot))`), but not for _L. guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`). However, because we suspect there may be a bias towards 'Blue' in the initial choice (see Supplementary Material and Figs. @Figdeli, @Figguich), we only used those individuals assigned to 'Red' to compare performance in the associative learning task. In this regard, we did not find any significant differences between treatments for _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich). When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`). We also did not find any significant differences when we compared the estimated slopes between species for the associative task (only individuals from 'Red' group: _L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).

```{r, Figdeli}
#| label: Figdeli
#| fig.cap: "Deli"
```

```{r, figguich}
#| label: Figguich
#| fig.cap: "Guich"
```

[RESULTS reversal]

## Discussion

## References
\printbibliography

\pagebreak

# Suplementary Material

#### Colour preference in the Associative task
To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution to get the predicted probability of choosing the right in the first trial using the formula: 
$$\text{Probability} = \frac{1}{1 + e^{-A}}$$

@@

  probright_drCORTCold_t = format_dec(mean(probright_drCORTCold), 3),
  probright_drControlCold_t = format_dec(mean(probright_drControlCold), 3),
  probright_drCORTHot_t = format_dec(mean(probright_drCORTHot), 3),
  probright_drControlHot_t = format_dec(mean(probright_drControlHot), 3),
  probright_dbCORTCold_t = format_dec(mean(probright_dbCORTCold), 3),
  probright_dbControlCold_t = format_dec(mean(probright_dbControlCold), 3),
  probright_dbCORTHot_t = format_dec(mean(probright_dbCORTHot), 3),
  probright_dbControlHot_t = format_dec(mean(probright_dbControlHot), 3),
  probright_grCORTCold_t = format_dec(mean(probright_grCORTCold), 3),
  probright_grControlCold_t = format_dec(mean(probright_grControlCold), 3),
  probright_grCORTHot_t = format_dec(mean(probright_grCORTHot), 3),
  probright_grControlHot_t = format_dec(mean(probright_grControlHot), 3),
  probright_gbCORTCold_t = format_dec(mean(probright_gbCORTCold), 3),
  probright_gbControlCold_t = format_dec(mean(probright_gbControlCold), 3),
  probright_gbCORTHot_t = format_dec(mean(probright_gbCORTHot), 3),
  probright_gbControlHot_t = format_dec(mean(probright_gbControlHot), 3)) %>%
gather(key = "column", value = "value", .) %>%
rename("prob_choice" = "value") %>%
# Then we build a df with the statistical test (one-tailed pmcmc) that the probability is >0.33 (the probability of choosing right by chance)
  probright_drCORTCold_t = format_dec(pmcmc(probright_drCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_drControlCold_t = format_dec(pmcmc(probright_drControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_drCORTHot_t = format_dec(pmcmc(probright_drCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_drControlHot_t = format_dec(pmcmc(probright_drControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbCORTCold_t = format_dec(pmcmc(probright_dbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbControlCold_t = format_dec(pmcmc(probright_dbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbCORTHot_t = format_dec(pmcmc(probright_dbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbControlHot_t = format_dec(pmcmc(probright_dbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grCORTCold_t = format_dec(pmcmc(probright_grCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grControlCold_t = format_dec(pmcmc(probright_grControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grCORTHot_t = format_dec(pmcmc(probright_grCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grControlHot_t = format_dec(pmcmc(probright_grControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbCORTCold_t = format_dec(pmcmc(probright_gbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbControlCold_t = format_dec(pmcmc(probright_gbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbCORTHot_t = format_dec(pmcmc(probright_gbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbControlHot_t = format_dec(pmcmc(probright_gbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3)) %>%
gather(key = "column", value = "value", .) %>%
rename("p_value" = "value") %>%
write.csv(comp_pval, file= "./output/Checking/comp_pval.csv")
# Now we merge them and organise them to have the final dt for the table
table_df <- merge(prob_df, comp_pval, by ="column") %>%

@@

                    labels = c("CORTCold" = "CORT-Cold", "ControlCold" = "Control-Cold", "CORTHot" = "CORT-Hot", "ControlHot" = "Control-Hot"))) %>%

@@

  select(-column) %>%
  pivot_wider(names_from = Group, values_from = c(prob_choice, p_value)) %>% #To split the df in Red and Blue
  select(Specie, Treatment, prob_choice_Blue, p_value_Blue, prob_choice_Red, p_value_Red) %>%
  arrange(Specie, Treatment) %>% # To arrange the rows the way I wantdata.frame()

@@

write.csv(table_df, file= "./output/Checking/table_df.csv")
#################

@@

  bold(~ `p_value_Blue` < 0.05, ~ `p_value_Blue` + prob_choice_Blue) %>%
  bold(~ `p_value_Red` < 0.05, ~ `p_value_Red` + prob_choice_Red) %>%

@@

  set_header_labels(prob_choice_Blue = "Prob Blue", 
                    p_value_Blue = "p-value Blue", 
                    prob_choice_Red = "Prob Red", 
                    p_value_Red = "p-value Red") %>%
  italic(j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics

@@

  vline(j = c(2,4), part = "all") %>% # To make some vertical lines on body
